### 2019-02-19 sections/introduction.tex
Fixed contributions in introduction

\input{sections/contributions}

@@

\begin{enumerate}

  \item
    We informally describe the essential concepts of task-oriented programming (\TOP).
    \TOP has a strong focus on modelling using collaboration
    while keeping a constant desire to rapidly generate executable applications into account.

  \item
    We present a formal calculus for \TOP, arising naturally from the aforementioned essential concepts.
    In doing so, we lay the ground work to allow formal reasoning about \TOP specifications in future work.

  \item
    Using both informal and formal descriptions, we compare \TOP and \TOPHAT with multiple related works in the areas,
    ranging from business process modelling languages, to process algebras and reactive programming frameworks.

\end{enumerate}

>>>>

\subsection{Scope}

In this paper, we set out to develop a formal basis for \TOP, called \TOPHAT (TopHat).
Our goal is to specify the basic building blocks of declarative workflows.
We clearly separate them from general purpose programming concepts.
This allows us to prove properties like progress and type preservation.
\TOPHAT should be powerful enough to model complicated real-world situations,
without losing opportunities for formal reasoning.

By separating them in the style of a deep embedding \cite{conf/cefp/Gibbons13}, we make explicit where and where not, they depend on each other. \fixme{what to do with this sentence}

We show that, where process algebras focus on the \emph{coordination} of processes and the \emph{communication} between them,
\TOP, and therefore \TOPHAT, focus on supporting \emph{tasks} and model ways to \emph{collaborate} on them.

@@

\begin{itemize}
  \item
    We informally describe the essential concepts of task-oriented programming (\TOP).

  \item
    We present a formal calculus for modelling declarative workflows, embedded in a simply typed lambda-calculus.
    This calculus is based on the aforementioned essential \TOP concepts.

  \item
    We develop an operational semantics that is driven by user input.
    The semantics of the task language is clearly separated from the semantics of the underlying host language.

  \item
    Along with the semantics, we present the following semantic observations on tasks:
    the current value, whether a term is stuck, the current user interface, and the accepted inputs. \fixme{we do not provide observation for user interface!}

  \item
    We implemented the whole semantic system in the dependently typed programming language Idris \cite{journals/jfp/Brady13}.

  \item
    We have implemented \TOPHAT in iTasks to demonstrate that the first is a subset of the second.

  \item
    Using both informal and formal descriptions, we compare \TOP with multiple related works in areas,
    ranging from business process modelling languages, to process algebras and reactive programming frameworks.

    \item
      We prove progress and type preservation for our calculus.

\end{itemize}
